Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-15 paper/manuscript.Rmd
update intro/results
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

classoption       : "man"
output            : papaja::apa6_word
---

@@

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. First, experts demonstrate what to be acquired and then novices reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities [@mermelshtine_2017]. This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by finding the specific problem of each novice from their unsuccessful attempts and modifying their behaviour accordingly [@ugur_2015; @zukow-goldring_2007].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults [@brand_2002]. Such exaggeration was observed not only towards infant learners but also when knowledgeable adults were interacting with adult learners [@mcellin_2017]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own.

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill level of learners [@fukuyama_2015]. In this study, mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. The mothers showed how to stack and fit the nesting cups so that infants could reproduce the actions by themselves. It was found that the mothers dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., in press), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

Evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action [@wood_1975; @zukow-goldring_2007]. Therefore, we hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing  louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

As predicted, there was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* `r if(leg_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* `r if(leg_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* `r if(leg_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`). Participants produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left).

@@

In line with our prediction, there was a significant main effect of Articulation (*F*(`r sta_all_aov$anova_table[1,1]`, `r sta_all_aov$anova_table[1,2]`) = `r sta_all_aov$anova_table[1,4]`, *p* `r if(sta_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r sta_all_aov$anova_table[2,1]`, `r sta_all_aov$anova_table[2,2]`) = `r sta_all_aov$anova_table[2,4]`, *p* `r if(sta_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', sta_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r sta_all_aov$anova_table[3,1]`, `r sta_all_aov$anova_table[3,2]`) = `r sta_all_aov$anova_table[3,4]`, *p* `r if(sta_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[3,5])`). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, right).

@@

Neither the main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* `r if(for_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', for_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', for_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* `r if(for_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* `r if(for_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`). Participants did not change their performances in terms of notated forte depending on the type of recordings (*Fig \ref{fig:vel-1}*, left).

@@

There was a significant main effect of Articulation (*F*(`r pia_all_aov$anova_table[1,1]`, `r pia_all_aov$anova_table[1,2]`) = `r pia_all_aov$anova_table[1,4]`, *p* `r if(pia_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r pia_all_aov$anova_table[2,1]`, `r pia_all_aov$anova_table[2,2]`) = `r pia_all_aov$anova_table[2,4]`, *p* `r if(pia_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r pia_all_aov$anova_table[3,1]`, `r pia_all_aov$anova_table[3,2]`) = `r pia_all_aov$anova_table[3,4]`, *p* `r if(pia_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[3,5])`). Participants produced softer piano when listening to the recordings where articulation was implemented (*Fig \ref{fig:vel-1}*, right).

@@

## KV Difference
### Forte to Piano

@@

These results indicated that participants did not change their performances in terms of dynamics contrast depending on the type of recordings (*Fig \ref{fig:vel-diff-1}*).

@@

Neither the main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* `r if(ioi_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* `r if(ioi_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* `r if(ioi_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`). This indicates that participants did not change the tempo depending on the type of recordings (*Fig \ref{fig:ioi-1}*).

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. First, experts demonstrate what novices are meant to acquired and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities [@mermelshtine_2017]. This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems of each novice from their unsuccessful attempts and modifying their behaviour accordingly [@ugur_2015; @zukow-goldring_2007].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults [@brand_2002].Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants’ learning when the infants failed to produce an expected action [@wood_1975; @zukow-goldring_2007]. @fukuyama_2015 performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that the mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills needed to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners [@mcellin_2017]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners’ demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research [@tominaga_2022], we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To gain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

We hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing  louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left). Accordingly, here was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* `r if(leg_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* `r if(leg_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* `r if(leg_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`).

@@

In line with our prediction, experts produced shorter staccato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, right). Accordingly, there was a significant main effect of Articulation (*F*(`r sta_all_aov$anova_table[1,1]`, `r sta_all_aov$anova_table[1,2]`) = `r sta_all_aov$anova_table[1,4]`, *p* `r if(sta_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r sta_all_aov$anova_table[2,1]`, `r sta_all_aov$anova_table[2,2]`) = `r sta_all_aov$anova_table[2,4]`, *p* `r if(sta_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', sta_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r sta_all_aov$anova_table[3,1]`, `r sta_all_aov$anova_table[3,2]`) = `r sta_all_aov$anova_table[3,4]`, *p* `r if(sta_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', sta_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', sta_all_aov$anova_table[3,5])`).

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (*Fig \ref{fig:vel-1}*, left). Neither the main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* `r if(for_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', for_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', for_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* `r if(for_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* `r if(for_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`).

@@

Experts produced softer piano only when listening to the recordings where articulation was implemented (*Fig \ref{fig:vel-1}*, right). There was a significant main effect of Articulation (*F*(`r pia_all_aov$anova_table[1,1]`, `r pia_all_aov$anova_table[1,2]`) = `r pia_all_aov$anova_table[1,4]`, *p* `r if(pia_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[1,5])`). However, there was no significant main effect of Dynamics (*F*(`r pia_all_aov$anova_table[2,1]`, `r pia_all_aov$anova_table[2,2]`) = `r pia_all_aov$anova_table[2,4]`, *p* `r if(pia_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r pia_all_aov$anova_table[3,1]`, `r pia_all_aov$anova_table[3,2]`) = `r pia_all_aov$anova_table[3,4]`, *p* `r if(pia_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', pia_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', pia_all_aov$anova_table[3,5])`).

@@

Unlike our prediction, experts did not change their performances in terms of dynamics contrast depending on the type of recordings (*Fig \ref{fig:vel-diff-1}*).

@@

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (*Fig \ref{fig:ioi-1}*). Neither the main effect of Articulation (*F*(`r ioi_all_aov$anova_table[1,1]`, `r ioi_all_aov$anova_table[1,2]`) = `r ioi_all_aov$anova_table[1,4]`, *p* `r if(ioi_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r ioi_all_aov$anova_table[2,1]`, `r ioi_all_aov$anova_table[2,2]`) = `r ioi_all_aov$anova_table[2,4]`, *p* `r if(ioi_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r ioi_all_aov$anova_table[3,1]`, `r ioi_all_aov$anova_table[3,2]`) = `r ioi_all_aov$anova_table[3,4]`, *p* `r if(ioi_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', ioi_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', ioi_all_aov$anova_table[3,5])`).
